The \dealii{} Library, Version 9.2

### 2020-06-01 9.2/paper.tex
add draft for step-50

  \item \texttt{step-50}
        \todo[inline]{Timo/Conrad/... to write}

>>>>

  \item \texttt{step-50} is a program that demonstrates the parallel geometric multigrid features
  in \dealii{} as described in \cite{ClevengerHeisterKanschatKronbichler2019}.
  The problem considered is a variable viscosity Laplace equation and it is solved
  with three different approaches:
  1. With a matrix-based geometric multigrid based on Trilinos or PETSc. 2. With a matrix-free
  geometric multigrid. 3. Using algebraic multigrid (Trilinos ML).

  \todo[inline]{Timo/Conrad/... to write}
